\documentclass{article}

% Doc info
\title{Multiple Heterogeneous Data Sources Integration for Discovery of Multiple Clustering Solutions}
\author{Yale Chang,	Jennifer Dy}

\begin{document}
\maketitle
\section{Abstract}
Dataset collected from multiple heterogeneous sources usually contains 
different data types and a complex dataset could be multi-faced by nature.
Most existing clustering algorithms, however, can only find a single solution
either by maximizing the clustering quality given one source or minimizing the
disagreement between different solutions given multiple sources. Moreover, 
existing work on exploring multiple clustering solutions can only use one 
single source as input. We introduce a novel approach that provides multiple
clustering solutions by integrating information from multiple heterogeneous 
data sources through multiple kernel learning. The objective is to preserve 
the global structure of data similarity matrix in dimensionality reduction as
well as finding good and novel clustering solutions. The data similarity 
matrix is constructed from convex linear combination of the similarity matrix
of each source. The novelty of a new clustering solution is measured by 
Hilbert-Schmidt independence criterion. The algorithm can automatically find
the weight of each source for every novel clustering solution. Experiment 
results show that our algorithm can find better and novel clustering solutions
by assigning different weights for each source.

\end{document}
